### 2013-07-15 doc/dissertation/document/chapters/nonlinear_problem/nonlinear_problem.tex
adding driven cavity solution figures

>>>>

Velocity magnitudes are given in
Figure~\ref{fig:driven_velocity_isocurves} for Reynolds numbers of
100, 300, 500 and 700. Increasing the velocity on the top boundary of
the problem drives up the Reynolds number of the system making it more
difficult to solve.  As the Reynolds number grows, momentum and energy
transport in the system is dominated by inertial forces rather than
viscous forces. More rotation of the fluid is induced by intertial
forces and we begin to see some additional vortices form besides the
primary vortex in the center of the box.

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/nonlinear_problem/driven_velocity_isocurves.png}
  \end{center}
  \caption{\textbf{Velocity magnitude isocurves from solution to the
      thermal convection cavity problem.} \textit{Top left: Re = 100;
      Top right: Re= 300; Bottom left: Re = 500; Bottom left: Re =
      700. Isocurves on unit velocity scale from 0 to 1 with divisions
      of 0.05 for each calculation.}}
  \label{fig:driven_velocity_isocurves}
\end{figure}
